Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-06-09 paper/paper.tex
Need more dollars

Due to the special structure of the maximum common subgraph problem, the following property holds
throughout the search process using the CP model: any two variables either have domains with no
values in common (with the possible exception of \bot), or have identical domains. The algorithm
McSplit exploits this property, while exploring essentially the same search tree as the CP model.
Rather than storing a domain for each vertex in $\operatorname{V}(G)$, which results in redundant
storage in cases where domains are identical, equivalence classes of vertices in
$\operatorname{V}(G)$ are stored, and a set of candidate vertices in $H$ is maintained for each
equivalence class. This enables fast propagation of the constraints and smaller memory requirements.
In addition, the data structure enables good branching heuristics to be calculated cheaply.

>>>>

Due to the special structure of the maximum common subgraph problem, the following property holds
throughout the search process using the CP model: any two variables either have domains with no
values in common (with the possible exception of $\bot$), or have identical domains. The algorithm
McSplit exploits this property, while exploring essentially the same search tree as the CP model.
Rather than storing a domain for each vertex in $\operatorname{V}(G)$, which results in redundant
storage in cases where domains are identical, equivalence classes of vertices in
$\operatorname{V}(G)$ are stored, and a set of candidate vertices in $H$ is maintained for each
equivalence class. This enables fast propagation of the constraints and smaller memory requirements.
In addition, the data structure enables good branching heuristics to be calculated cheaply.
